\chapter{The Air Fryer}
\label{chap:air-fryer}

\epigraph{
\twonotes~If you've got no time in the morning,\\
And you wanna make a beautiful breakfast,\\
Then put these things in an air fryer,\\
And out comes a beautiful breakfast!~\eighthnote
}{@airfryerguy, TikTok}

\section{Breakfast}
\label{sec:air-fryer-breakfast}

% =========================================================================== %
% Air Fryer Egg McMuffin                                                      %
% =========================================================================== %
\begin{recipe}{Air Fryer Egg McMuffin}{1 serving}{8 min.}
\freeform Here's a pretty decent recipe for a copycat Egg McMuffin that I
sussed out one morning after several failed attempts at using other recipes.
It's dead easy --- all you need is an air fryer and a small ramekin (sort of
a round porcelain dish that is oven-safe).

\Ing{One large egg}
\Ing{One English muffin}
\Ing{Cheddar cheese, to taste}
\Ing{One \enquote{glug} of cooking oil}
Brush cooking oil around the bottom of the ramekin. Crack one large egg
into the ramekin. Place the ramekin into the air fryer. Cut English muffin
in half and place both sides face up in the air fryer. Place cheese on top of
one half of the English muffin.  Fry at 350\0F for 4 minutes.

\Ing{One slice Canadian bacon}
Remove English muffins from the air fryer and replace them with Canadian bacon.
Leave the eggs in the air fryer and fry once more at 350\0F for 4 minutes.

\newstep Assemble the Egg McMuffin and enjoy.
\end{recipe}

\section{Lunch}
\label{sec:air-fryer-lunch}

\clearpage

\section{Dinner}
\label{sec:air-fryer-dinner}

\clearpage

\section{Dessert}
\label{sec:air-fryer-dessert}

\clearpage
